The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-22 paper.tex
update

The simulated gamma-ray and microwave spectra is based on the\
IC scattering and synchrotron from CRe, respectively, in which\
the CRe spectrum follows a power-law distribution ranging from\
$0.5$ MeV to $562.1$ GeV.

@@

where $\Gamma$ is gamma function, $B$ is the magnetic field strength defined in\
\Cref{magnetic-field}.

>>>>

The simulated gamma-ray and microwave spectra is based on the\
IC scattering and synchrotron, respectively, from CRe.\
The CRe spectrum follows a power-law distribution ranging from\
$0.5$ MeV to $562.1$ GeV.

@@

where $\Gamma$ is the gamma function, $B$ is the magnetic field strength defined in\
\Cref{magnetic-field}.
